\section{Related Work}
A very effective method for solving path planning problems is to reformulate the original problem
into an equivalent one in a much smaller abstract search space. 
Known as hierarchical path planning this approach has been well studied over the last decade;
algorithms in this category are usually fast, memory-efficient and suboptimal.
Our contribution follows this general idea while seeking to retain optimality.
It is perhaps most similar to the popular HPA* algorithm \cite{botea04} 
which divides a grid map into a series of fixed-size clusters connected 
by entrances.
Finding a shortest path then involves inserting the start and goal into the 
abstract graph and searching for a (usually suboptimal) path between them.
\par
Our work also bears some similarity to a recent result outlining new heuristic methods for improving the 
performance of standard A* on games maps \cite{bjornsson06}.
In that work, much like in ours, grid maps are decomposed into obstacle-free zones connected by entrances 
and exits. 
A preprocessing step identifies zones containing entrances but no corresponding exits, thus
yielding the \emph{dead-end heuristic} (a similiar yet orthogonal idea to our main result).
A highly informed \emph{gateway heuristic} is also developed which requires computing and storing exact 
costs between all pairs of entrances and exits.
Both heuristics are shown to be admissible and yield optimal length paths. 
Average running time improvements over standard A* are reported at between 10-40\% using a range of
realistic games maps.
\par
Another algorithm with similar goals to our work is Fringe Search \cite{bjornsson05}.
Fringe Search is a general purpose iterative deepening search algorithm with memory requirements
comparable to A*. 
It is provably optimal if maximum search depth is sufficiently large and, crucially, has been shown to 
run between 25-40\% faster than A*.
