\section{Conclusion}

Traditional speed-up techniques for pathfinding on grid maps 
include hierarchical abstraction and memory-based heuristics.
While effective, both types of approaches have their shortcomings.
Hierarchical algorithms such as HPA*~\cite{botea04} and PRA*~\cite{sturtevant07}
are fast and memory-effective but produce sub-optimal paths.
Memory-based admissible heuristics preserve the optimality of 
solutions but carry a significant memory overhead~
\cite{sturtevant09,goldberg05,Cazenave:06,bjornsson06}.

Recent work~\cite{pochter10,harabor10} has introduced
techniques that are fast, produce optimal solutions and
require little additional memory.
In this paper we have introduced RSR,
an algorithm that converts an initial map
into a smaller search graph without sacrificing the optimality of solutions.
Similarly to \citeauthor{harabor10}'s approach~\shortcite{harabor10},
our algorithm uses a decomposition of a map into disjoint rectangular
rooms with the property that no room contains obstacle tiles.
All interior tiles and some of the perimeter tiles 
(except for start and target locations)
are pruned from search.

In experiments our algorithm is not only more generally applicable
than \citeauthor{harabor10}'s algorithm~\shortcite{harabor10},
but also significantly faster on the set of instances where both
methods can be applied (i.e., 4-connected maps).
Our analysis reveals that RSR and swamps~\cite{pochter10}
have complementary strengths and therefore there are many
instances where RSR is the better choice.
Swamps appear to be more useful in areas with small open areas.
RSR becomes more effective as larger open areas are available on a map.

%OPTIONAL: 
%Have here a brief summary of speed-up numbers:
%Overall, the best speed-ups we have observed for RSR are blah.
%On the same data, swamps achieve a maximal speed-up of blah.
%Harabor and Botea's method has a speed-up of blah.

Future work includes reducing the branching factor in RSR further.
We have observed cases where the number of expanded nodes is reasonably small
but a relatively large branching factor increases the number of visited nodes significantly.
Another interesting topic is combining swamps and RSR, which tend to complement each other.
We are also interested in applying our ideas to more general types of graphs that exhibit
(local) symmetry, such as the search graphs of planning instances.


%Perimeter Search is a symmetric path elimination technique which extends the the
%work of \citeauthor{harabor10}~\shortcite{harabor10} from 4-connected grid maps
%to the much more common 8-connected case.
%We speed up optimal pathfinding by applying an offline decomposition algorithm to
%divide a grid map into a series of empty rectangular rooms.
%We then show that it is possible to traverse optimally from one side of a room
%to another without exploring any tiles from the interior of any room.
%Our experiments show that in the presence of large rooms or wide open areas we can 
%compute optimal paths very quickly: up to 16 times faster, on average for 4-connected maps and up to
%6.5 times faster, on average, for 8-connected maps.
%On less favourable map topographies we achieve more modest improvements.
%Our method is simple to understand, very effective and can be combined with
%existing speedup techniques such as memory heuristics or hierarchical methods;
%for example as described in \cite{botea04,bjornsson05,bjornsson06}. 
%\par
%One direction for future work is to investigate alternative decomposition
%algorithms which produce bigger rooms and improve the performance of the current
%method.

