\section{Conclusion}
In this paper we develop a new online node pruning strategy for speeding up
pathfinding on grid maps.  Our algorithm identifies and selectively expands only
certain nodes from a grid map which we call \emph{jump points}.  Moving between
jump points involves only travelling in a fixed direction, either straight or
diagonal.  We prove that intermediate nodes on a path between two jump points
never need to be expanded and ``jumping'' over them does not affect the
optimality of search.
\par
Our method is unique in the pathfinding literature in that it has very few
disadvantages: it is simple, yet highly effective; it preserves optimality, yet
requires no extra memory;  it is extremely fast, yet requires no preprocessing.
Further, our method is completely orthogonal to and easily combined with 
competing speedup techniques from the literature.
We are unaware of any other algorithm which has all these features.
\par
To evaluate our new technique we perform a wide range of experiments on a number
synthetic and real-world benchmarks, including two taken from the popular video
games \emph{Baldur's Gate II: Shadows of Amn} and \emph{Dragon Age: Origins}.
We show that in each case jump point pruning is many times faster than Swamps
\cite{pochter10}, a recent state-of-the-art optimality preserving pruning
technique.  We also show that jump point pruning is competitive with, and in
many instances faster than, HPA*; a popular though sub-optimal pathfinding
technique which is often employed in performance sensitive applications such as
video games.
\par
One interesting direction for further work is to combine jump points with other
speedup techniques such as Swamps and HPA* to achieve better results.
Another direction is to generalise the jump points method to weighted grid maps.
