\subsection{Algorithmic Description}
We begin by making precise the concept of a jump point.  
To do so, we use the notation $\vec{d}$ 
to refer to one of the eight unit moves that can be taken from a node.  
We write $y = x + k_{x}\vec{d}$ when node~$y$ can be reached 
by taking $k_{x}$ unit moves from node~$x$ in direction $\vec{d}$.
According to the pruning rules defined above, 
if move~$\vec{d}$ from node~$p(x)$ to node~$x$ is diagonal, 
then two straight moves are enabled from node~$x$ 
(see Figure~\ref{fig:pruning}(c)); 
these two moves are denoted by $\vec{d_1}$ and $\vec{d_2}$.  

\begin{definition}
\label{def:jump}
Node~$y$ is the \emph{jump point} from node~$x$ heading in direction~$\vec{d}$ 
if it minimises the value $k_x$ such that $y = x + k_{x} \vec{d}$ and one of the following conditions holds: 
\begin{enumerate}
\item{Node~$y$ is the goal node.}
\item{Node~$y$ has at least one neighbour whose evaluation is forced according 
to Definition \ref{def:forced}.}
\item{$\vec{d}$ is a diagonal move and there exists 
a node $z = y + k_{y} \vec{d_{i}}$ which lies in direction $\vec{d_i} \in \{\vec{d_1},\vec{d_2}\}$ s.t
$z$ satisfies condition 1 or condition 2 }
\end{enumerate}
\end{definition}

Figure \ref{fig:jumppoints}(b) shows an example of a jump point which is
identified by way of condition 3.
Here we start at $x$ and travel diagonally until encountering node $y$. 
We identify $y$ as a jump point of $x$ by applying condition 3 of 
Definition \ref{def:jump}. This in turn invokes condition 2 to identify $z$ 
as a jump point from $y$.

\input alg_jumpexpansion

The process by which we generate the set of successors during the expansion of 
node $x$ is given in Algorithm \ref{alg:successors}.
We start with the pruned set of neighbours immediately adjacent to $x$ (line 3).
Then, instead of immediately adding each neighbour $n$ to the set of successors
for $x$, we try to ``jump'' to a node that is further away but which lies in the 
same relative direction to $x$ as $n$ (lines 4:5). 
For example, if the edge $(x, n)$ constitutes a
straight move travelling \emph{right} from $x$, we look for a jump point among
the nodes immediately to the right of $x$.
If we find such a node, we add it to the set of successors instead of $n$.
In the case where we fail to find a jump point, we add nothing.
The process continues until the set of neighbours for $x$ is exhausted.

In order to identify individual successors for $x$ we will apply Algorithm
\ref{alg:jump} which requires an initial node (here $x$) a direction of travel
$\vec{d}$ (e.g. up, down, left, right, etc.), 
the start node $s$ and the goal node $g$.
In rough overview, the algorithm attempts to establish whether $x$ has any 
jump point successors by stepping in the direction $\vec{d}$ and testing
if the node $n$ at that location satisfies Definition \ref{def:jump}.
When this is the case, $n$ is designated a jump point and returned (lines 5, 7
and 11).
When $n$ is not a jump point the algorithm recurses and steps again in direction
$\vec{d}$ but this time $n$ is the new initial node (line 12).
The recursion terminates when an obstacle is encountered and no further
steps can be taken (line 3).
Note that before each diagonal step the algorithm must first 
fail to detect any straight jump points (lines 9:11). 
This check corresponds to the third condition of Definition \ref{def:jump} 
and is essential for preserving optimality.
