\section{Related Work}
\label{sec:relatedwork}
Dealing with symmetry is a regularly appearing topic in the literature.  It has
been addressed in areas as diverse as planning \cite{fox99}, constraint programming
\cite{gent00}, and combinatorial optimization \cite{fukunaga08}.  This is not
surprising given that, in the presence of symmetry, search algorithms often
evaluate many equivalent states and make little real progress toward the goal.
Despite receiving significant attention in other areas, there are very few
works that explicitly identify and deal with symmetry in pathfinding domains 
such as grid maps. 
\par
The work most closely related to ours is Empty Rectangular Rooms
\cite{harabor10}: a symmetry breaking technique specific to 4-connected
uniform-cost grid maps which we will refer to as 4ERR.  We discuss the main
differences between 4ERR and RSR in Sections \ref{sec:introduction} and
\ref{sec:rsr}.
\par
The \emph{dead-end heuristic} \cite{bjornsson06} and \emph{Swamps-based
pathfinding} \cite{pochter10} are two closely-related graph pruning techniques
that involve the same central idea: to identify areas in the search space that
are not relevant for reaching the goal. This is a similar yet complementary goal
to RSR, which tries to reduce the search effort involved in exploring any given
area.  The dead-end heuristic, like RSR, proceeds by decomposing the map into a
series of obstacle-free rooms connected by entrances and exits.  A preliminary
online search in the decomposed graph is then used to identify so called ``dead
ends'' -- rooms that can be ignored during a subsequent search in the original
grid as exploring them is not necessary to reach the goal.  A stronger variant
of this idea is used in \cite{pochter10}.
This time the objective is to decompose the map into a set of so 
called \emph{Swamp} areas. Nodes in a Swamp can be ignored as there always
exists a set of symmetric paths that never cross the Swamp.  To achieve a
speedup, each search instance is limited to a corridor of provably relevant
Swamp and non-Swamp areas and all remaining nodes in the graph are ignored.
\par
The \emph{gateway heuristic} \cite{bjornsson06} and the \emph{portal heuristic}
\cite{goldenberg10} are two similar memory-based techniques which also attempt
to speed up optimal pathfinding on grid maps.  Like RSR, they too proceed to
decompose the map into a series of adjacent areas.  Both then pre-compute a
database of exact distances between all pairs of nodes that transition from area
to another (called variously ``'portals'' or ``gates'').  The main idea
is to use this information to improve the accuracy of cost-to-go estimates
during search as a way of reducing the number states expanded by A* on the way
to the goal. Where the portal heuristic differs from other similar works
\cite{bjornsson06,sturtevant09,felner09} is in its use of the decomposed
graph to further prune the state space. This is done via preliminary online 
search in the decomposed graph that identifies portals relevant to
the search instance at hand. Any nodes in an area that contains no relevant
portals are ignored.
\par
In the algorithm engineering community the problem of quickly computing optimal
shortest paths has received significant attention.  State of the art methods
such as TRANSIT \cite{bast06} and Contraction Hierarchies \cite{geisberger08}
are based on a combination of Dijkstra's algorithm together with
memory-intensive abstractions that reduce the search space by way of node
elimination or the introduction of short-cut edges.  Such algorithms are very
fast but they are also highly optimised for road networks in which certain
topological properties hold true: for example, the existence of ``highway''
edges that appear on most shortest paths between arbitrary pairs of nodes.
Though mostly orthogonal to RSR, there has been very little work applying these
ideas to searching on grid maps. One recent result however \cite{sturtevant10}
suggests they are not as effective when the underlying graph contains a high
degree of path symmetry.
