\section{Problem Definition}
A \emph{gridmap} is a structure composed of square cells, of unit size, each of which represent a unique area in the environment. 
Each grid cell is an \emph{octile}, connected to $k$ neighbours, where  $0 \leq k \leq 8$. 
\par \indent
Each octile, $t$, is associated with a particular terrain type, $terrain(t) \in T$ where $T$ is the set of all possible terrains and there are $r = |T| : r \geq 1$ possible terrains.
Each octile is either blocked or traversable. 
Blocked octiles are called \emph{hard obstacles}, since no agent can occupy them.
\par \indent
Each gridmap is representable as a graph, $G = (V, E)$ where each traversable tile generates one node $v \in V$ and each cell adjacency is represented by an edge $e \in E$.
\par \indent
An \emph{agent} is any entity attempting to move across a grid environment. 
Every agent is square in shape and has a size $s \geq 1 : s \in S$ where $S$ is the set of finite sizes agents traversing across the gridmap may take.
While stationary or moving, each agent occupies $s^2$ octiles which together correspond to its current location. 
\par \indent
Agents can move in any of the four cardinal directions. 
Diagonal moves are allowed only if there exists an equivalent two-step move using the cardinal directions.
\par \indent
Every agent has a terrain traversal \emph{capability}, $c \in C$, where $c$ comprises a non-empty subset of terrains.
An agent can never occupy a tile whose terrain type is not included in its capability.
\par \indent 
A \emph{soft obstacle} is a tile which is not traversable by a specific agent because it lacks the correct capability or its size is larger than the associated clearance value of the tile, as defined below. 
\par \indent
A \emph{clearance value} is an obstacle-distance metric associated with a particular tile in the grid environment. 
Each clearance value measures the maximal size of an agent at a given location without intersecting any obstacle in the environment. 
A tile can have several clearance values associated with it, one for each capability. 
\par \indent
A \emph{problem instance} is defined as a pair of locations, a start and goal, associated with an agent. A problem is valid if at least one path exists between the locations comprising only tiles traversable by the agent. 
